Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/main-supplementary-material.tex
Move content from related work to supp. material

@@

>>>>

% Comment 
% FIXME : delete before submission :)
\newcommand{\bertrand}[1]{\textcolor{violet}{Bertrand:~#1}}
\newcommand{\nathalie}[1]{\textcolor{purple}{Nathalie:~#1}}
\newcommand{\edwin}[1]{\textcolor{pink}{Edwin:~#1}}
\newcommand{\joseph}[1]{\textcolor{red}{Joseph:~#1}}

@@

\subsection{Entry segmentation}

\subsection{Line detection}
Pero OCR uses ParseNet as internal layout parser for line detection.
Pero OCR uses an LSTM engine for text line recognition.
Pero OCR generally works very well, as long as the bounding boxes of the regions to recognize are not too tightly adjusted.
Trained on newspapers in European languages by its development team.
Can output results in Latin, Greek and Cyrillic scripts, as well as some commonly-used typographic symbols.

### 2022-01-20 src-latex/parts/20-related-work.tex
Move content from related work to supp. material

@@

\begin{itemize}
    \item Tesseract 4.1.1 (newest version: 5, released Nov. 2021)
    \item Pero OCR version from git repo, master branch updated on Sep 15, 2021 % 8b20f29    
    \item other?  % kraken if times allows
\end{itemize}
Pero OCR uses ParseNet \joseph{TODO ref} as internal layout parser for line detection.
Pero OCR uses an LSTM engine \joseph{TODO check + ref} for text line recognition.
Pero OCR generally works very well, as long as the bounding boxes of the regions to recognize are not too tightly adjusted.
Trained on newspapers in European languages by its development team.
Can output results in Latin, Greek and Cyrillic scripts, as well as some commonly-used typographic symbols.

>>>>

\joseph{Suggestion pour réduire la présentation de l'état de l'art : l'orienter exclusivement vers une justification des systèmes que nous avons retenus pour cet article.}

@@

\joseph{Move to implementation details for XP OCR or to pipeline summary}
\begin{itemize}
    \item Tesseract 4.1.1 (newest version: 5, released Nov. 2021)
    \item Pero OCR version from git repo, master branch updated on Sep 15, 2021 % 8b20f29    
    \item other?  % kraken if times allows
\end{itemize}
